My title

### 2024-12-01 paper/paper.qmd
Model and Data Edits

library(tidyverse)

@@

# 2024
NBA2024 <- read.csv("../data/01-raw_data/All NBA/AllNBA_2024.csv", header = FALSE)
new_col_names <- as.character(unlist(NBA2024[2, ]))
NBA2024 <- NBA2024[-c(1, 2), ]
colnames(NBA2024) <- new_col_names
NBA2024[] <- lapply(NBA2024, type.convert, as.is = TRUE)
```

@@

    # Calculate MVP index, now including WS
    dataset$MVP_index <- 0.5 * dataset$norm_PTS +
                         0.2 * dataset$norm_AST +
                         0.2 * dataset$norm_TRB +
                         0.1 * dataset$norm_WS  # Adjust weights as needed

@@

@@

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

>>>>

library(tidyverse)
library(dplyr)
library(janitor)
library(lubridate)
library(modelsummary)
library(rstanarm)
library(knitr)
library(bayesplot)
```

@@

# 2024
NBA2024 <- read.csv("../data/01-raw_data/All NBA/AllNBA_2024.csv", header = FALSE)
new_col_names <- as.character(unlist(NBA2024[2, ]))
NBA2024 <- NBA2024[-c(1, 2), ]
colnames(NBA2024) <- new_col_names
NBA2024[] <- lapply(NBA2024, type.convert, as.is = TRUE)

@@

    # Calculate MVP index, now including WS
    dataset$MVP_index <- 0.8 * dataset$norm_PTS +
                         0.25 * dataset$norm_AST +
                         0.25 * dataset$norm_TRB +
                         0.1 * dataset$norm_BLK +
                         0.1 * dataset$norm_STL +
                         0.15 * dataset$norm_WS  # Adjust weights as needed

@@

nba_list <- list()

for (year in years) {
  dataset_name <- paste0("NBA", year)
  dataset <- get(dataset_name)
  dataset$Year <- year
  nba_list[[as.character(year)]] <- dataset
}

nba_master <- do.call(rbind, nba_list)
write.csv(nba_master, "../data/nba_master.csv", row.names = FALSE)

@@

```{r}
bay_model <- stan_glm(
  MVP_index ~ PTS + AST + TRB + BLK + STL + WS,
  data = nba_master,
   family = gaussian(),
  prior = normal(0, 5),
  prior_intercept = normal(0, 5),
  chains = 4,
  iter = 2000,
  warmup = 1000,
  cores = 4,
  control = list(adapt_delta = 0.95),
  seed = 613
)
